---
title: "R Project 1 - Hello R"
author: "Alana Valdez"
date: "9/16/2020"
output: 
  html_document: 
    fig_width: 10
    fig_height: 9
    highlight: espresso
    theme: cerulean
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

#information based on ? datasauRus
/
1846 rows
3 columns
variables = "dataset, x, y"

### Exercise 2

#plot the data in the dino dataset
```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#calculate the correlation between `x` and `y` in this dataset:
```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

#plot the data in the away dataset
```{r plot-away, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "away")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


#Away is about four ten-thousandths larger than dino
 
#calculate the correlation between `x` and `y` in away  dataset:
```{r cor-away}
dino_data %>%
  summarize(r = cor(x, y))
```
### Exercise 4


#plot the data in the bullseye dataset
```{r plot-bullseye, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "bullseye")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
#calculate the correlation between `x` and `y` in bullseye dataset:
```{r cor-bullseye}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5
#plot of all datasets
```{r plot-dozen, fig.height=3, fig.width=6}
ggplot(datasaurus_dozen, aes(x = x, y = y, color =dataset)) +
  geom_point()+
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

#calculate the correlation between `x` and `y` in all datasets
```{r cor-dozen}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```



